Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-21 articles/cycle/alps-cycle.tex
Subdivide results section.

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \item Maximum extent is farily well reproduced (Fig.~\ref{fig:lgmvel}a).
    \item Maximum extent is time-transgressive (Fig.~\ref{fig:timing}).
    \item Glaciers have different response times (Fig.~\ref{fig:timing}).
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}

>>>>

    In this section, we compare the model output to geological evidence from
    the last glacial cycle, in terms of LGM extent (Sect.~\ref{sec:extent}),
    ice flow patterns (Sect.~\ref{sec:flow}), ice thickness
    (Sect.~\ref{sec:thickness}), timing (Sect.~\ref{sec:timing}), and the
    number of glaciations (Sect.~\ref{sec:glaciations}).

    This simulation is forced by the optimal EPICA palaeo-temperature record
    (Sect.~\ref{sec:paltemp}) and includes palaeo-precipitation reduction
    (Sect.~\ref{sec:palprec}). It uses an horizontal resolution of 1\,km. The
    vertical grid consists of 61~temperature layers in the bedrock and up to
    251~enthalpy layers in the ice, corresponding to vertical resolutions of 50
    and 20\,\unit{m}, respectively.

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM extent}
\label{sec:extent}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Maximum extent is farily well reproduced (Fig.~\ref{fig:lgmvel}a).
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM flow pattern}
\label{sec:flow}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM ice thickness}
\label{sec:thickness}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Ice surface is well above the trimlines (Fig.~\ref{fig:lgmvel}a).
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Timing of the LGM}
\label{sec:timing}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Maximum extent is time-transgressive (Fig.~\ref{fig:timing}).
    \item Glaciers have different response times (Fig.~\ref{fig:timing}).
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Number of glaciations}
\label{sec:glaciations}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}
